paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

### Results
Our replication confirms the primary result of Brown et al. (2020). We found that highly restrictive legislation is associated with 0.814 fewer abortions per 1,000 women without adjusting for distance to providers, and 0.649 fewer abortions per 1,000 women when adjusting for distances to providers.  These effects are somewhat larger in magnitude than the effects calculated by Brown et al., which were -0.48 (95% CI, -0.92 to -0.04) and -0.44 (95% CI, -0.85 to -0.03), but our estimates were well within their reported 95% confidence intervals.

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2]*1000, 
                           model_dist$coefficients[3]*1000,
                           model_dist$coefficients[4]*1000),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1000*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1000*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1000*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1000*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1000*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1000*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Abortion Rate per 1,000 Women in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```
### Extension to Infant Death Rate, Birth Rate, and Fertility Rate
We found positive associations between abortion restrictions and both birth rates and fertility rates (see Tables 9-12), however these associations were not statistically significant after adjusting for distance to providers, with p-values > 0.5.

>>>>

### Results
Our replication confirms the primary result of Brown et al. (2020). We found that highly restrictive legislation is associated with 0.814 fewer abortions per 1,000 women without adjusting for distance to providers, and 0.649 fewer abortions per 1,000 women when adjusting for distances to providers.  These effects are somewhat larger in magnitude than the effects calculated by Brown et al., which were -0.48 (95% CI, -0.92 to -0.04) and -0.44 (95% CI, -0.85 to -0.03), but our estimates were well within their reported 95% confidence intervals. Infant mortality rates were positively associated with abortion restrictions, and these associations were statistically significant even after adjusting for distance from providers.  The maternal and fetal mortality rates were not statistically significant.

@@

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2]*1000, 
                           model_dist$coefficients[3]*1000,
                           model_dist$coefficients[4]*1000),
                  "95% CI lower" = c(model_dist$coefficients[2,1]*1000-model_dist$coefficients[2,2]*1000*1.96,
                                     model_dist$coefficients[3,1]*1000-model_dist$coefficients[3,2]*1000*1.96,
                                     model_dist$coefficients[4,1]*1000-model_dist$coefficients[4,2]*1000*1.96),
                  "95% CI upper" = c(model_dist$coefficients[2,1]*1000+model_dist$coefficients[2,2]*1000*1.96,
                                     model_dist$coefficients[3,1]*1000+model_dist$coefficients[3,2]*1000*1.96,
                                     model_dist$coefficients[4,1]*1000+model_dist$coefficients[4,2]*1000*1.96),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Abortion Rate per 1,000 Women in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```
### Extension to Infant Death Rate, Birth Rate, and Fertility Rate
We found positive associations between abortion restrictions and both birth rates and fertility rates (see Tables 9-12), however these associations were not statistically significant after adjusting for distance to providers, with p-values > 0.5.  Infant mortality rates were positively associated with abortion restrictions, and these associations were statistically significant even after adjusting for distance from providers (see Tables 13 and 14) .  The maternal and fetal mortality rates were not statistically significant (see Tables 15-18).
